---
title: "CVglasso"
output: github_document
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
```

[![R-CMD-check](https://github.com/jmcurran/CVglasso/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jmcurran/CVglasso/actions/workflows/R-CMD-check.yaml)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/CVglasso)](https://cran.r-project.org/package=CVglasso)

## Note

**NOTE:** This package was created by Matt Galloway. James Curran only the current maintainer to keep it on CRAN; credit belongs to 
the original author.


## Overview

`CVglasso` is an R package that estimates a lasso-penalized precision matrix via block-wise coordinate descent -- also known as the graphical lasso (glasso) algorithm. This package is a simple wrapper around the popular [glasso](https://cran.r-project.org/web/packages/glasso/index.html) package and extends and enhances its capabilities. These enhancements include built-in cross validation and visualizations.

<p align="center">
  <img src = "https://github.com/jmcurran/CVglasso/raw/master/vignettes/images/gif.gif"/>
</p>

A (possibly incomplete) list of functions contained in the package can be found below:

* `CVglasso()` computes the estimated precision matrix

* `plot.CVglasso()` produces a heat map or line graph for cross validation errors

See package [website](https://jmcurran.github.io/CVglasso/) or [manual](https://github.com/jmcurran/CVglasso/blob/master/CVglasso.pdf).

## Installation

```{r, eval = FALSE}
# The easiest way to install is from CRAN
install.packages("CVglasso")

# You can also install the development version from GitHub:
# install.packages("devtools")
devtools::install_github("jmcurran/CVglasso")
```

If there are any issues/bugs, please file them on [GitHub](https://github.com/jmcurran/CVglasso/issues). Pull requests are welcome!

## Usage

```{r, message = FALSE}
library(CVglasso)
set.seed(123)

# generate data from a sparse oracle precision matrix
# we will try to estimate this matrix from the data

# first compute the oracle covariance matrix
S = matrix(0.7, nrow = 5, ncol = 5)
for (i in 1:5){
  for (j in 1:5){
    S[i, j] = S[i, j]^abs(i - j)
  }
}

# print oracle precision matrix (shrinkage might be useful)
(Omega = round(qr.solve(S), 3))

# generate 100 x 5 matrix with rows drawn from iid N_p(0, S)
set.seed(123)
Z = matrix(rnorm(100*5), nrow = 100, ncol = 5)
out = eigen(S, symmetric = TRUE)
S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
X = Z %*% S.sqrt

# calculate sample covariance
sample = (nrow(X) - 1)/nrow(X)*cov(X)

# print sample precision matrix (perhaps a bad estimate)
round(qr.solve(cov(X)), 5)


# CVglasso (lam = 0.5)
CVglasso(S = sample, lam = 0.5)

# cross validation
(CV = CVglasso(X, trace = "none"))

# produce line graph for CV errors for CVGLASSO
plot(CV)

# produce CV heat map for CVGLASSO
plot(CV, type = "heatmap")

```
